# Baselines 

## For New Profiles



```{r older,cache=TRUE,include=FALSE}
v2 <- versions[, {
    s1 <- .BY$date
    s2 <- .BY$date+6
    V <- .BY$version
    list(j = d0[pcd >=s1 & pcd<=s2,][, list(v = version[1]) ,by=cidf][, sum(v<V)/.N*100])
},by=list(version,date)]
xmins <- round(range(v2$j),2)
```

### First Week

For context, the following figures are first week measures for new profiles.
For example in the first figure, we plot the session length/day/profile against
the day the profile was created. Overlaid is the a smooth line fitted to 7 day
rolling averages. The dotted red lines correspond to version releases. Bear in
mind that after a version is released between `r xmins[1]` and `r xmins[2]`  % of new profiles are on
older versions (in the first week since profile creation).


```{r plotbase,cache=TRUE}

pl <- function(v,s1,main,cutOut=1,xaxs='pcd',xlab='Profile Creation Date',xlim=NULL)
{ 
    u= xyplot(get(v)  ~ get(xaxs), xlab=xlab
         , ylab=''
         , type=c('l')
         , scale=list(x=list(tick.num=25,cex=0.6,rot=45,format='%Y-%m-%d'),
                      y=list(tick.num=10)
                      )
          , data=s1[get(v)<=quantile(get(v),cutOut),]
          , col='#cccccc'
          , panel=function(x,y,...){
              panel.grid(v=0)
              panel.xyplot(x,y,...)
              y2=as.numeric(filter (y, rep(1,7)/7))
              for(i in 1:nrow(versions)){
                  panel.abline(v=versions[i,date],lty=3,col='red')
              }
              panel.loess(x,y2,type='l',col='black',span=0.25,lwd=1.5)
          },main=main
          )
   if(!is.null(xlim)) u <- update(u,xlim=xlim)
   u
}
```


```{r makePlot,cache=TRUE,dependson=c('newOn'),fig.align='center',fig.width=8}
s1 <-  d0[sh<=24 & pcd>='2016-08-08' & pcd<='2017-12-01' & date >=pcd  & date<=(pcd+6),]
s11 <- s1[,{    list(s=any( sh>0 ))},by=list(pcd,cidf)][,list(s=mean(s)),by=pcd][order(pcd),]
pl("s",s11,"First Week Retention")
```

```{r sessionbase,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
s2 <- s1[,{    list(s=sum(sh)/.N)},by=list(pcd,cidf)][,list(s=mean(s)),by=pcd][order(pcd),]
pl("s",s2,"Session Hours/Day/Profile")
```


```{r intensbase,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
s3 <- s1[,{    list(s=sum(ah,na.rm=TRUE)/(sum(sh,na.rm=TRUE)+C))},by=list(pcd,cidf)][,list(s=mean(s)),by=pcd][order(pcd),]
pl("s",s3,"Intensity/Profile")
```


```{r tabsbase,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
s4 <- s1[,{    list(s=sum(tabsopened)/(sum(sh,na.rm=TRUE)+C))},by=list(pcd,cidf)][,list(s=mean(s)),by=pcd][order(pcd),]
s4 <- s4[pcd>='2017-03-01',]
pl("s",s4,"Tabs & Windows Opened/Hour/Profile",cut=0.995)
```


```{r urisbase,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
s5 <- s1[,{   list(s=sum(uris)/(sum(sh,na.rm=TRUE)+C))},by=list(pcd,cidf)][,list(s=mean(s)),by=pcd][order(pcd),]
s5 <- s5[pcd>='2017-03-01',]
pl("s",s5,"URIs  Opned/Hour/Profile",cut=0.995)
```


```{r searchesbase,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
s6 <- s1[,{    list(s=sum(search)/(sum(sh,na.rm=TRUE)+C))},by=list(pcd,cidf)][,list(s=mean(s)),by=pcd][order(pcd),]
pl("s",s6,"Searches Made/Hour/Profile",cut=0.995)
```


```{r crate0base,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
s7 <- s1[,{    list(s=any(cr>0))},by=list(pcd,cidf)][,list(s=mean(s)),by=pcd][order(pcd),]
s7 <- s7[pcd>='2017-08-01',]
pl("s",s7,"# Profiles Crashing in Opening Week")
```

```{r crate1base,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
s8 <- s1[,{    list(s=sum(crash)/sum(sh,na.rm=TRUE)*1000)},by=list(pcd)][order(pcd),]
s8 <- s8[pcd>='2017-08-01',]
pl("s",s8,"Crash Rate (Definition 2)")
```


### Second Week

Retention and crash propensity  is only in the second week, everything else is
cumulative till second week.

```{r makePlot2,cache=TRUE,dependson=c('newOn'),fig.align='center',fig.width=8}
s1aa <- d0[sh<=24 & pcd>='2016-08-08' & pcd<='2017-12-01' & date >=(pcd)  & date<=(pcd+13),]
s11 <- s1aa[,{    list(s=any( sh[date>=(pcd+7) & date<=(pcd+13)] >0 ))},by=list(pcd,cidf)][,list(s=mean(s)),by=pcd][order(pcd),]
pl("s",s11,"Second Week Retention")
```

```{r sessionbaesecond,cache=TRUE,dependson=c('newOn'),fig.align='center',fig.width=8}
s1a <- d0[sh<=24 & pcd>='2016-08-08' & pcd<='2017-12-01' & date >=(pcd)  & date<=(pcd+13),]
s2 <- s1a[,{    list(s=sum(sh)/.N)},by=list(pcd,cidf)][,list(s=mean(s)),by=pcd][order(pcd),]
pl("s",s2,"Session Hours/Day/Profile")
```


```{r intensbasesecond,cache=TRUE,dependson=c('sessionbaesecond','newOn'),fig.align='center',fig.width=8}
s3 <- s1a[,{    list(s=sum(ah,na.rm=TRUE)/(sum(sh,na.rm=TRUE)+C))},by=list(pcd,cidf)][,list(s=mean(s)),by=pcd][order(pcd),]
pl("s",s3,"Intensity/Profile")
```


```{r tabsbasesecond,cache=TRUE,dependson=c('sessionbaesecond','newOn'),fig.align='center',fig.width=8}
s4 <- s1a[,{    list(s=sum(tabsopened)/(sum(sh,na.rm=TRUE)+C))},by=list(pcd,cidf)][,list(s=mean(s)),by=pcd][order(pcd),]
s4 <- s4[pcd>='2017-03-01',]
pl("s",s4,"Tabs & Windows Opened/Hour/Profile",cut=0.995)
```


```{r urisbasesecond,cache=TRUE,dependson=c('sessionbaesecond','newOn'),fig.align='center',fig.width=8}
s5 <- s1a[,{   list(s=sum(uris)/(sum(sh,na.rm=TRUE)+C))},by=list(pcd,cidf)][,list(s=mean(s)),by=pcd][order(pcd),]
s5 <- s5[pcd>='2017-03-01',]
pl("s",s5,"URIs  Opned/Hour/Profile",cut=0.995)
```

```{r crate0basesecond,cache=TRUE,dependson=c('makePlot2','newOn'),fig.align='center',fig.width=8}
s7 <- s1aa[,{    list(s=any(cr[date>=(pcd+7) & date<=(pcd+13)]>0))},by=list(pcd,cidf)][,list(s=mean(s)),by=pcd][order(pcd),]
s7 <- s7[pcd>='2017-08-01',]
pl("s",s7,"# Profiles Crashing in Second Week")
```

```{r crate1basesecond,cache=TRUE,dependson=c('sessionbaesecond','newOn'),fig.align='center',fig.width=8}
s8 <- s1a[,{    list(s=sum(crash)/sum(sh,na.rm=TRUE)*1000)},by=list(pcd)][order(pcd),]
s8 <- s8[pcd>='2017-08-01',]
pl("s",s8,"Crash Rate (Definition 2)")
```




## For Existing profiles

### First Week

Consider profiles created at least two weeks before a date and their typical
behavior in a week as of that date. These are the baselines

```{r baselineExist,eval=TRUE,cache=TRUE}
d01 <- d0[date>='2017-01-01',d0[sh<=24 & pcd<=(.BY$date-13) & date>=(.BY$date) & date<=(.BY$date+6),
                                list(sh=sum(sh,na.rm=TRUE)/.N,
                                     inten=sum(ah,na.rm=TRUE)/(sum(sh,na.rm=TRUE)+C),
                                     tabs=sum(tabsopened)/(sum(sh,na.rm=TRUE)+C),
                                     uris=sum(uris)/(sum(sh,na.rm=TRUE)+C),
                                     crashed=any(cr>0)),by=cidf][, list(sh=mean(sh),
                                                                        inten=mean(inten),
                                                                        tabs=mean(tabs),
                                                                        uris=mean(uris),
                                                                        crashed=mean(crashed))]
         ,by=date]

dcr <- d0[date>='2017-01-01',d0[sh<=24 & pcd<=(.BY$date-13) & date>=(.BY$date) & date<=(.BY$date+6),
                                list(s=sum(crash)/sum(sh,na.rm=TRUE)*1000)]
         ,by=date]
save(d0, newonv,versions,exisd,FAC,d01,dcr, file="~/tmp/snapshot.Rdata")
```


```{r sessionbase2,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
e2 <- d01[,list(date=date,s=sh)][order(date),]
pl("s",e2,"Session  Hours/Day/Profile",xaxs='date',xlab='Date')
```


```{r intenbasd2,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
e2 <- d01[,list(date=date,s=inten)][order(date),]
pl("s",e2,"Intensity per /Profile",xaxs='date',xlab='Date ')
```

```{r tabsbase2,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
e2 <- d01[,list(date=date,s=tabs)][order(date),]
pl("s",e2,"Tabs + Windows Opened/ Hr/Profile",xaxs='date',xlab='Date ',cut=0.995)
```

```{r urisbase2,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
e2 <- d01[,list(date=date,s=uris)][order(date),]
pl("s",e2,"URIS visited/hr/Profile",xaxs='date',xlab='Date ',cut=0.995)
```



```{r crasherbase2,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
e2 <- d01[,list(date=date,s=crashed)][order(date),][date>='2017-08-01',]
pl("s",e2,"Proportion of Crashers",xaxs='date',xlab='Date ')
```

```{r crasherbase3,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
e2 <- dcr[order(date),][date>='2017-08-01',]
pl("s",e2,"CRash Rate (Definition 2) crashes/1000hrs" ,xaxs='date',xlab='Date ',cut=0.995)
```

### Second Week

Consider profiles created at least two weeks before a date and their typical
behavior for two  week as of that date. These are the baselines. Retention and
crash prop is only for second week but everything else is cumulative for two
weeks.


```{r baselineExist2,eval=TRUE,cache=TRUE}
invisible({d0 <- d0[, ":="(dend1=date-13,dend2=date+13,dmid=date+7)]})
d01w2 <- d0[date>='2017-01-01' & sh<=24,
{
    d1 <- dend1[1]; d2 <- dend2[1];d3=dmid[1]
    XX <- .BY$date
    x <- d0[pcd<=d1 & date>=XX & date<=d2,
            list(sh=sum(sh,na.rm=TRUE)/.N,
                 inten=sum(ah,na.rm=TRUE)/(sum(sh,na.rm=TRUE)+C),
                 tabs=sum(tabsopened)/(sum(sh,na.rm=TRUE)+C),
                 uris=sum(uris)/(sum(sh,na.rm=TRUE)+C),
                 crt=sum(crash),
                 ret=any(sh [date>=d3] >0), crashed=any(cr[date>=d3] >0))
                ,by=cidf]
    x[, list(sh=mean(sh), inten=mean(inten), tabs=mean(tabs), uris=mean(uris), ret=mean(ret),crash=mean(crash)
           , crate =sum(crt)/sum(sh)*1000)]
},by=date]
save(d0, newonv,versions,exisd,FAC,d01,dcr,d01w2,file="~/tmp/snapshot.Rdata")
```


```{r retbase3,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
e2 <- d01w2[,list(date=date,s=ret)][order(date),]
pl("s",e2,"Retetion in 2nd week",xaxs='date',xlab='Date')
```


```{r sessionbase3,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
 e2 <- d01w2[,list(date=date,s=sh)][order(date),]
pl("s",e2,"Session  Hours/Day/Profile",xaxs='date',xlab='Date',cut=0.995)
```


```{r intenbasd3,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
 e2 <- d01w2[,list(date=date,s=inten)][order(date),]
pl("s",e2,"Intensity per /Profile",xaxs='date',xlab='Date ',cut=0.995)
```

```{r tabsbase3,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
 e2 <- d01w2[,list(date=date,s=tabs)][order(date),]
pl("s",e2,"Tabs + Windows Opened/ Hr/Profile",xaxs='date',xlab='Date ',cut=0.995)
```

```{r urisbase3,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
 e2 <- d01w2[,list(date=date,s=uris)][order(date),]
pl("s",e2,"URIS visited/hr/Profile",xaxs='date',xlab='Date ',cut=0.995)
```



```{r crasherbase21,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
 e2 <- d01w2[,list(date=date,s=crash)][order(date),][date>='2017-08-01',]
pl("s",e2,"Proportion of Crashers (2nd Week)",xaxs='date',xlab='Date ',cut=0.99)
```

```{r crasherbase4,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
 e2 <- d01w2[,list(date,s=crate)][order(date),][date>='2017-08-01',]
pl("s",e2[s>=0,],"CRash Rate (Definition 2) crashes/1000hrs" ,xaxs='date',xlab='Date ',cut=0.995)
```
