# Baselines



```{r older,cache=TRUE,include=FALSE}
v2 <- versions[, {
    s1 <- .BY$date
    s2 <- .BY$date+6
    V <- .BY$version
    list(PctNewProfileOnOlderVersion = d0[pcd >=s1 & pcd<=s2,][, list(v = version[1]) ,by=cidf][, sum(v<V)/.N*100])
},by=list(version,date)]
xmins <- round(range(v2$PctNewProfileOnOlderVersion),2)
```

## First Week

For context, the following figures are first week measures for new profiles.
For example in the first figure, we plot the session length/day/profile against
the day the profile was created. Overlaid is the a smooth line fitted to 7 day
rolling averages. The dotted red lines correspond to version releases. Bear in
mind that after a version is released between `r xmins[1]` and `r xmins[2]`  % of new profiles are on
older versions (in the first week since profile creation).


```{r makePlot,cache=TRUE}
pl <- function(v,s1,main,cutOut=1){
    xyplot(get(v)  ~ pcd, xlab='Profile Creation Date'
         , ylab=''
         , type=c('l')
         , scale=list(x=list(tick.num=25,cex=0.6,rot=45,format='%Y-%m-%d'),
                      y=list(tick.num=10)
                      )
          , data=s1[get(v)<=quantile(get(v),cutOut),]
          , col='#cccccc'
          , panel=function(x,y,...){
              panel.grid(v=0)
              panel.xyplot(x,y,...)
              y2=as.numeric(filter (y, rep(1,7)/7))
              for(i in 1:nrow(versions)){
                  panel.abline(v=versions[i,date],lty=3,col='red')
              }
              panel.loess(x,y2,type='l',col='black',span=0.25,lwd=1.5)
          },main=main)
}
s1 <- d0[sh<=24 & pcd>='2016-08-08' & pcd<='2017-12-01' & date >=pcd  & date<=(pcd+6),]
```


```{r retbase,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
s11 <- s1[,{    list(s=any( sh>0 ))},by=list(pcd,cidf)][,list(s=mean(s)),by=pcd][order(pcd),]
pl("s",s11,"First Week Retention")
```

```{r sessionbase,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
s2 <- s1[,{    list(s=sum(sh)/.N)},by=list(pcd,cidf)][,list(s=mean(s)),by=pcd][order(pcd),]
pl("s",s2,"Session Hours/Day/Profile")
```


```{r intensbase,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
s3 <- s1[,{    list(s=sum(ah,na.rm=TRUE)/(sum(sh,na.rm=TRUE)+C))},by=list(pcd,cidf)][,list(s=mean(s)),by=pcd][order(pcd),]
pl("s",s3,"Intensity/Profile")
```


```{r tabsbase,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
s4 <- s1[,{    list(s=sum(tabsopened)/(sum(sh,na.rm=TRUE)+C))},by=list(pcd,cidf)][,list(s=mean(s)),by=pcd][order(pcd),]
s4 <- s4[pcd>='2017-03-01',]
pl("s",s4,"Tabs & Windows Opened/Hour/Profile",cut=0.995)
```


```{r urisbase,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
s5 <- s1[,{   list(s=sum(uris)/(sum(sh,na.rm=TRUE)+C))},by=list(pcd,cidf)][,list(s=mean(s)),by=pcd][order(pcd),]
s5 <- s5[pcd>='2017-03-01',]
pl("s",s5,"URIs  Opned/Hour/Profile",cut=0.995)
```


```{r searchesbase,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
s6 <- s1[,{    list(s=sum(search)/(sum(sh,na.rm=TRUE)+C))},by=list(pcd,cidf)][,list(s=mean(s)),by=pcd][order(pcd),]
pl("s",s6,"Searches Made/Hour/Profile",cut=0.995)
```


```{r crate0base,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
s7 <- s1[,{    list(s=any(cr>0))},by=list(pcd,cidf)][,list(s=mean(s)),by=pcd][order(pcd),]
s7 <- s7[pcd>='2017-08-01',]
pl("s",s7,"# Profiles Crashing in Opening Week")
```

```{r crate1base,cache=TRUE,dependson=c('makePlot','newOn'),fig.align='center',fig.width=8}
s8 <- s1[,{    list(s=sum(crash)/sum(sh,na.rm=TRUE)*1000)},by=list(pcd)][order(pcd),]
s8 <- s8[pcd>='2017-08-01',]
pl("s",s8,"Crash Rate (Definition 2)")
```

