# Existing Users


## Period of Study

Once a profile updates to 57(in the first week of release), what does their
subsequent two weeks look like?

## Acquisition

```{r exis2retention, cache=TRUE}
exisd[,list(RetentionSecondWeek=mean(actpo2)), by=list(date,version)][order(version),]
```

## Session Length/Profile/Day

```{r exis2session, cache=TRUE}
exisd[,list(AverageSessionLength=mean(shpoall/npoall)) , by=list(date,version)][order(version),]
```

## Intensity/Profile

```{r exis2inten, cache=TRUE}
exisd[,list(Intensity=mean(ahpoall/(C+shpoall))), by=list(date,version)][order(version),]
```

## Tabs and Windows Opened

```{r exis2tabs, cache=TRUE}
exisd[,list(TabsOpenedPerHour=mean(tabpoall/(C+shpoall))), by=list(date,version)][order(version),]
```

## URIs visited

```{r exis2uri, cache=TRUE}
exisd[,list(UriSVisitedPerHour=mean(uripoall/(C+shpoall))), by=list(date,version)][order(version),]
```

## Crash Propensity

Only for the second week.

```{r exis2crashd, cache=TRUE}
exisd[,list(CrashPropensity=mean(crpoall)), by=list(date,version)][order(version),]
```


## Crash Rates

```{r exis2crashd2, cache=TRUE}
exisd[,list(CrashRateDefinition2=sum(crashpoall)/sum(shpoall)*1000), by=list(date,version)][order(version),]
```

## Lapsed Users

The definition of a lapsed user is one who was on two or more older versions.
What percentage of these profiles update to a given version? We extend this for
2,3, and 4 versions or older. 

We consider profiles who updated in the 14 days since version release.

```{r lapsed1, cache=TRUE}
options(width=1000)
lapsedUsers <- versions[, {
    s1 <- .BY$date
    s2 <- .BY$date+14
    V <- .BY$version
    a= d0[date>=s1 & date<=s2 & version==V, data.table(cidf=unique(cidf))]
    b = merge(d0[,list(cidf,date,version)],a, by='cidf')[ date<s1 & date >=(s1-210) & version < V,]
    b[, list(l2 = 1*((V-max(version))>=2),l3=1*((V-max(version))>=3), l4=1*((V-max(version))>=4)) ,  by=cidf]
},by=list(date,version)]
lapsedUsers[, list(PropOn2PlusOlder=mean(l2),PropOn3PlusOlder=mean(l3),PropOn4PlusOlder=mean(l4)), by=list(date,version)]
```

What is there *retention rate*? We look at it for profiles 3  or more versions
older

```{r lapsed2, cache=TRUE,dependson='lapsed1'}
options(width=1000)
retentionForLapsed3 <- versions[,{
    lapsedUser2 <- merge(d0, lapsedUsers[l3==1 & version==.BY$version,list(cidf)],by='cidf')
    lapsedUser2[version==.BY$version,{
    o1 <- .SD[ as.numeric((date - min(date))) %between% c(0,6), any(sh>0)]
    o2 <- .SD[ as.numeric((date - min(date))) %between% c(7,13), any(sh>0)]
    list(week1=o1,week2=o2)
    },by=cidf][,list(week1prop=mean(week1), week2prop=mean(week2))]
}, by=list(date,version)]
retentionForLapsed3
```


## Do Low Usage Users Move to a Higher Usage?

A question asked is *does a low usage profile move to a higher usage after
updating?*, the open questions are 

- what is low usage profile?
- if it has increased do 
  - we see the same phenomena in other versions 
  - is it because of seasonality? 

One way to tackle the first is do the same analysis across multiple versions and
for the second we can 

- use total session length in two weeks (if they used it more, then this would
  have gone up)
- to handler seasonality, we can segment profiles previous use (the two weeks
  prior to update) into 10 deciles and do the same for post usage (the following
  two weeks). Thus has a profile in the lower percentiles (say bottom three)
  moved to higher percentiles. Effectively this removes the dependency on actual
  value of session length: if seasonality is present, a users session length
  might well decrease but they will likely (if nothing changes) still remain in
  the same percentile(or close to it). There is the issue of the population
  changing i.e. my usage didnt change at all but i became a 'low user' because
  of an influx of higher usage profiles. We will assume this doesn't happen in
  small periods of time


Before start  a model, we can see 

- partition everyone's  pre-version usage (the usage 2 weeks prior to update) into
  10 percentiles
- see how they migrate from bottom 40% to a bucket 4 percentiles
  higher(e.g. from group 1 to group 4 or more)
- compute the average across versions and see where 57 lies

```{r churn1,cache=TRUE}
invisible({
    exisd2 <- exisd[version>=51,]
    exisd2[,":="(
        preCut = as.numeric(cut(shpre, quantile(shpre,seq(0,1,length=11)),include=TRUE)),
        poallCut = as.numeric(cut(shpoall, quantile(shpre,seq(0,1,length=11)),include=TRUE))
    ),by=list(version)]
    ax <- exisd2[,  list(d=list(x=prop.table(table(preCut, poallCut),1))), by=version]
    s=0
    for(i in 1:nrow(ax)){
        s <- s+ax[i,d][[1]]
    }
})
```

The average transition probabilities (percentage of pre usage percentile group
moving to higher (the columns))
```{r}
(savg <- round(s/nrow(ax)*100,0))
```

In particular for profiles  in percentiles 1 to 4(which contribute to less than
3% of usage), what % move 4 or more percentiles higher? Well on average (across
different version updates) we have `sum(unlist(lapply(1:4, function(k) sum(savg[k, (k+4):10]))))`% and 
given other versions, 57 looks typical

```{r}
ax[,{
    son=round(d[[1]]*100,0)
    list(upBy4=sum(unlist(lapply(1:4, function(k) sum(son[k, (k+4):10])))))
} ,by=version][order(version)]
```


Does  profiles on 57 tend to move to higher percentiles after
update?  We can a build a logistic model testing the indicator *did a low user
profile, move to a higher percentile* after update?

We'll use low usage group as the bottom 4 percentiles *'moving up'* is if they
moved up by 4 percentiles . Looking at the output below, it seems  that none of
the versions are remarkably different from each other.

```{r  cache=TRUE}
invisible({exisd2[, up:= (poallCut - preCut)>=4]})
m2 <- glm(up ~ factor(version), data=exisd2[preCut<=4,], family='binomial')
summary(m2)
```
