# New Profiles

Recall we are working with a 0.1% sample. Very few of our figure will have actual counts.

## Period of Study

We consider the first week since a version is released and the three weeks
thereafter. Retention is measured separately for every week, every other measure
is cumulative across weeks.

## Acquisition

How many profiles do we usually acquire in the period? This is based on profile
creation date and a more accurate view is the *new profile ping*, however we
lack history for this ping.

```{r newcount, cache=TRUE, dependson='newonv'}
a <- newonv[,list(release=release[1],nprofiles = FAC*length(unique(cidf))) ,by=version][order(version),]
a
```

## Retention 

The definition of retention is whether a profile used the browser.
Not using the definition that uses URIs since that doesnt exist prior to 2017.

```{r retention,cache=TRUE,dependson='newonv'}
isn <- function(s,subcode=NA) if(is.null(s) || length(s)==0) subcode else s
a1 <- newonv[,{
    oneday <- isn(1*any((active[daysSince==1])),0)
    week1 <- isn(1*any(active[daysSince %between% c(0,6)]),0)
    week2 <- isn(1*any(active[daysSince %between% c(7,13)]),0)
    week3 <- isn(1*any(active[daysSince %between% c(14,20)]),0)
    data.table(period=c('oneday','week1','week2','week3'),active=c(oneday,week1,week2,week3))
},by=list(version,cidf)]
a1 <- a1[,list(active=sum(active)*FAC) ,by=list(version,period)]
a1 <- merge(a,a1,by='version')[,retention:=active/nprofiles][,][order(period,version),]
a1 <- a1[period %in% c("oneday","week1","week2"),][,list(version,release,period,retention=retention*100)]
a1 <- reshape(a1,dir='wide', v.names='retention',timevar='period',idvar=c('version','release'))
a1 

```

## Session Length / Profile / Day 

```{r session, cache=TRUE,dependson='newonv'}
a2 <- newonv[sh<=24, {
    w1 <- isn(sum(sh[daysSince %between% c(0,6)]),0)
    w2 <- isn(sum(sh[daysSince %between% c(0,13)]),0)
    w3 <- isn(sum(sh[daysSince %between% c(0,20)]),0)
    d1 <- sum(daysSince %between% c(0,6))
    d2 <- sum(daysSince %between% c(0,13))
    d3 <- sum(daysSince %between% c(0,20))
    if(d1==0) w1 <- 0
    if(d2==0) w2 <- 0
    if(d3==0) w3 <- 0
    data.table(period=c('week1','week2','week3'),sessionlength=c(w1/(0.001+d1),w2/(0.001+d2),w3/(0.001+d3)))
},by=list(version,cidf)]
a2 <- a2[, list(sessionlength=mean(sessionlength)),by=list(version,period)]
a2 <- merge(a,a2,by='version')[order(period,version),]
a2 <- a2[period %in% c("oneday","week1","week2"),][,list(version,release,period,sessionlength)]
a2 <- reshape(a2,dir='wide', v.names='sessionlength',timevar='period',idvar=c('version','release'))
a2

```


## Intensity / Profile

The ratio of the active ticks (in hours) to the total usage (aggregated to the
given period). The higher the value, more 'involved' the profile is (e.g. a lot
of mouse movement,page scrolling, clicking on things  etc)

```{r simpleTables,include=FALSE}
mt <- function(vname,modi=1){
    a3 <- newonv[sh<=24, {
        v1 <- get(vname)
        x1 <- isn(sum(v1[daysSince %between% c(0,6)]),0)
        x2 <- isn(sum(v1[daysSince %between% c(0,13)]),0)
        x3 <- isn(sum(v1[daysSince %between% c(0,20)]),0)
        s1 <- isn(sum(sh[daysSince %between% c(0,6)]),0)
        s2 <- isn(sum(sh[daysSince %between% c(0,13)]),0)
        s3 <- isn(sum(sh[daysSince %between% c(0,20)]),0)
        data.table(period=c('week1','week2','week3'),x=c(x1/(C+s1),x2/(C+s2),x3/(C+s3))*modi  )
    },by=list(version,cidf)]
    a3 <- a3[, list(x=mean(x),xlow=quantile(x,0.15),xhigh=quantile(x,0.85)),by=list(version,period)]
    a3 <- merge(a,a3,by='version')[order(period,version),]
    a3 <- a3[period %in% c("week1","week2"),][,list(version,release,period,x,xlow,xhigh)]
    a3 <- reshape(a3,dir='wide', v.names=c('x','xlow','xhigh'),timevar='period',idvar=c('version','release'))
    setnames(a3,c("version",'release','week1Avg','week1Low','week1Hi','week2Avg','week2Low','weel2Hi'))
    a3
}
```


```{r intens, cache=TRUE,dependson='newonv'}
options(width=1000)
(intensdf <- mt('ah'))
```


## Tabs and Windows Opened

Number of tabs and window opened per hour per profile. This field was not
present in 2016.

```{r tabsopened, cache=TRUE,dependson='newonv'}
options(width=1000)
tabdf <- mt("tabs")
tabdf[release>'2017-03-01',]
```



## URIs visited

The number of  URIs visited per hour per profile. URI measure was not present in 2016.

```{r urivisit, cache=TRUE,dependson='newonv'}
options(width=1000)
tabdf <- mt("uris")
tabdf[release>'2017-03-01',]
```




## Crash Propensity

The definition of a crash is if `C` defined as 

```
C = crash_submit_success_main+(crashes_detected_content-shutdown_kill)
```

is positive. Note that `crash_submit_success_main` is biased below the true
number of browser crashes. This measures the proportion of profiles
experiencing a crash in a given time period.


```{r crashprop,cache=TRUE,dependson='newonv'}

a4 <- newonv[,{
    oneday <- isn(1*any((cr[daysSince==1])),0)
    week1 <- isn(1*any(cr[daysSince %between% c(0,6)]),0)
    week2 <- isn(1*any(cr[daysSince %between% c(7,13)]),0)
    week3 <- isn(1*any(cr[daysSince %between% c(14,20)]),0)
    data.table(period=c('oneday','week1','week2','week3'),crashq=c(oneday,week1,week2,week3))
},by=list(version,cidf)]
a4 <- a4[,list(crashq=sum(crashq)*FAC) ,by=list(version,period)]
a4 <- merge(a,a4,by='version')[,crashprop:=crashq/nprofiles][,][order(period,version),]
a4 <- a4[period %in% c("oneday","week1","week2"),][,list(version,release,period,crashprop=crashprop*100)]
a4 <- reshape(a4,dir='wide', v.names='crashprop',timevar='period',idvar=c('version','release'))
options(width=1100 )
a4

```

## Crash Rates

### Definition 1

We compute the crash rate (total content and browser crashes removing shutdowns
per hour)  for a profile and then average this across profiles. The
interpretation: "pick a profile at random, then the value below is crash rate
for a typical profile".


```{r crate1, cache=TRUE,dependson='newonv'}
options(width=1000)
cr1df <- mt('crash',mod=1000)
cr1df[release>'2017-08-01',]
```


### Definition 2

This is the definition used by [https://www.arewestableyet.com/dashboard/]
(table on the right, 'M+C-S'). It is defined as the total crashes divided the
total profile hours. The interpretation is "choose a random profile weighted by
the hours of use in the week, then the value below is their crash rate" (with
the data i have i can’t compute the percentiles)

```{r crate2, cache=TRUE,dependson='newonv'}
a8 <- newonv[sh<=24, {
    x1 <- isn(sum(crash[daysSince %between% c(0,6)]),0)
    x2 <- isn(sum(crash[daysSince %between% c(0,13)]),0)
    x3 <- isn(sum(crash[daysSince %between% c(0,20)]),0)
    s1 <- isn(sum(sh[daysSince %between% c(0,6)]),0)
    s2 <- isn(sum(sh[daysSince %between% c(0,13)]),0)
    s3 <- isn(sum(sh[daysSince %between% c(0,20)]),0)
    data.table(period=c('week1','week2','week3'),crashRate=c(x1/(C+s1),x2/(C+s2),x3/(C+s3))*1000) 
},by=list(version)]
a8 <- merge(a,a8,by='version')[order(period,version),]
a8 <- a8[period %in% c("week1","week2"),][,list(version,release,period,crashRate)]
a8 <- reshape(a8[release>='2017-08-01',], dir='wide', v.names='crashRate',timevar='period',idvar=c('version','release'))
options(width=1000)
a8
```
